Higher-Order unification for free!

### 2024-04-17 paper/main.tex
solve a todo

\begin{proof}[Proof sketch]\todo{to reformulate}
  % For any step $i$, we want to prove that $\fstep_i$ succeeds iff $\hstep_i$
  % succeeds. A $\hstep_i$ is made by a unification
  % $u = \sigma_{i-1}\hoUnifPb_{i_l} \Ue \sigma_{i-1}\hoUnifPb_{i_r} \mapsto \sigma_i'$ and a link
  % progression $p = \progress(\linkStore_{i-1},\sigma_i') \mapsto (\linkStore_i,\sigma_i)$.
  For any step $i$, we want to prove that $\fstep_i$ succeeds iff $\hstep_i$
  succeeds. A $\hstep_i$ is made by a unification $u$ and a link
  progression $p$.
  Without loss of generality,\todo{explain why} we consider a
  \Fo unification problem of the form $s_1 \Uo s_2$
  where $s_1 \in \maybeeta$. $s_1$ is compiled to $X$ with the accessory link
  $\linketaM{\Gamma}{X}{\lambda x.t_1}$. 
  The unification $u$ always succeeds, since $X$ is a fresh variable, we 
  only have to consider the link progression $p$.
  Two cases should be analyzed:
  \begin{itemize}
    \item $s_2 \notin \maybeeta$,
          in this case $s_2$ is compiler to $t_2$ and $u$ assigns $t_2$ to $X$
          and triggers \progressetaleft if $t_2$ is rigid.
          If $s_1$ and $s_2$ unify thanks to \ref{clause:eta1} then
          progression $p$ unifies $\lambda x.t_1$ with the $\eta$-expansion of $t_2$ namly
          $\lambda x.t_2\appsep x$, otherwise they unify thanks to lam-lam\todo{dare nome}
          and $p$ unifies $\lambda x.t_1$ with $t_2$. Alternatively, if $s_1$ and $s_2$ fails
          to unify, it cannot be because of the head $\lambda$ constructors,
          since wither lam-lam or \ref{clause:eta1} move under it and find
          different sub terms $s_1'$ and $s_2'$. By \cref{th:fidelity-beta},
          \Ue fails on terms $t_1'$ and $t_2'$ even if \progressetaleft
          $\eta$-expands $t_2$.

>>>>

\begin{proof}[Proof sketch]\todo{to reformulate}
  % For any step $i$, we want to prove that $\fstep_i$ succeeds iff $\hstep_i$
  % succeeds. A $\hstep_i$ is made by a unification
  % $u = \sigma_{i-1}\hoUnifPb_{i_l} \Ue \sigma_{i-1}\hoUnifPb_{i_r} \mapsto \sigma_i'$ and a link
  % progression $p = \progress(\linkStore_{i-1},\sigma_i') \mapsto (\linkStore_i,\sigma_i)$.
  For any step $i$, we want to prove that $\fstep_i$ succeeds iff $\hstep_i$
  succeeds. A $\hstep_i$ is made by a unification $u$ and a link
  progression $p$.
  Without loss of generality,\todo{explain why} we consider a
  \Fo unification problem of the form $s_1 \Uo s_2$
  where $s_1 \in \maybeeta$. $s_1$ is compiled to $X$ with the accessory link
  $\linketaM{\Gamma}{X}{\lambda x.t_1}$. 
  The unification $u$ always succeeds, since $X$ is a fresh variable, we 
  only have to consider the link progression $p$.
  Two cases should be analyzed:
  \begin{itemize}
    \item $s_2 \notin \maybeeta$,
          in this case $s_2$ is compiler to $t_2$ and $u$ assigns $t_2$ to $X$
          and triggers \progressetaleft if $t_2$ is rigid.
          If $s_1$ and $s_2$ unify thanks to \ref{clause:eta1} then
          progression $p$ unifies $\lambda x.t_1$ with the $\eta$-expansion of $t_2$ namly
          $\lambda x.t_2\appsep x$, otherwise they unify thanks to \cref{clause:lam-lam}
          and $p$ unifies $\lambda x.t_1$ with $t_2$. Alternatively, if $s_1$ and $s_2$ fails
          to unify, it cannot be because of the head $\lambda$ constructors,
          since wither lam-lam or \ref{clause:eta1} move under it and find
          different sub terms $s_1'$ and $s_2'$. By \cref{th:fidelity-beta},
          \Ue fails on terms $t_1'$ and $t_2'$ even if \progressetaleft
          $\eta$-expands $t_2$.
